\documentclass[11pt]{article}

\usepackage[letterpaper]{geometry}

\usepackage[utf8]{inputenc}
\usepackage{mathpazo}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{physics}
\usepackage{siunitx}

\usepackage{fancyhdr}

\usepackage{graphicx}
\usepackage{float}
\usepackage{booktabs}

\usepackage[shortlabels,inline]{enumitem}

% Hyperlinks with decent looking default colors.
\usepackage{hyperref}
\usepackage{xcolor}
\hypersetup{
  colorlinks,
  linkcolor={red!50!black},
  citecolor={blue!50!black},
  urlcolor={blue!80!black}
}

% For those sexy spaced low small caps from classic-thesis!
\usepackage{microtype}
\usepackage{textcase}
\DeclareRobustCommand{\spacedlowsmallcaps}[1]{%
  \textls[80]{\scshape\MakeTextLowercase{#1}}%
}

\pagestyle{fancy} 
\fancyhead{}
\rhead{Ali Ramadhan}
\lhead{12.818: Project 3}
\chead{}
\cfoot{\thepage}

\title{\spacedlowsmallcaps{\small 12.818: Introduction to Atmospheric Data and Large-scale Dynamics}\\ \spacedlowsmallcaps{\Large Project three: Convection and atmospheric thermodynamics}}
\author{\spacedlowsmallcaps{Ali Ramadhan}}
\date{}

% \renewcommand\thesection{\Alph{section}}

\begin{document}
\maketitle

In this project we will use the concept of hydrostatic balance to estimate the \emph{tilt} of isobaric pressure surfaces in the atmosphere from the poles to the equator. The monthly/seasonal composite plots in this project were produced using NCEP\footnotemark~reanalysis data averaged from Janurary 1948 to August 2017.  The Earth System Research Laboratory of the Physical Sciences Division of NOAA provides a convenient \href{ https://www.esrl.noaa.gov/psd/cgi-bin/data/composites/printpage.pl}{web page} for producing these plots.

\begin{thebibliography}{9}
\bibitem{AMSVirtualTemp}
American Meteorological Society, cited 2012: Virtual temperature. Glossary of Meteorology. [Available online at \url{http://glossary.ametsoc.org/wiki/Virtual_temperature}]

\bibitem{Wallace}
Wallace, John M. and Peter V. Hobbs. \textit{Atmospheric Science; An Introductory Survey}. Elsevier. Second Edition, 2006. Chapter 1.
\end{thebibliography}

\end{document}